A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-06-07 main.tex
Wrote a paragraph of 多段階計算のメリットをべき乗の例を用いて説明する.

\subsubsection{多段階計算とは何か?}

@@

\subsubsection{CSPに関する補足説明}
Cross-stage Persistence (CSP) is another primitive of multistage programming, which enable us to embed computed values into a code value.
This is an example of CSP.
\begin{verbatim}
        let plusone = fun x -> x + 1 in
        let a = plusone 2 in  .< a >.
\end{verbatim}
This program evaluates to \verb|.< 3 >.| not  \verb|.< plusone 2 >.|.
This is because the variable \verb|a| is introduced into a code fragment using CSP.
Therefore, the variable \verb|a| is embeded after \verb|a| is calculated.
CSP is very important when we write practival programs 
because CSP enables us to use library functions in code fragments.

\subsubsection{多段階計算のメリットをべき乗の例を用いて説明する}

The main application of multistage calculi is program optimization.

>>>>

% \subsubsection{多段階計算とは何か?}

@@

% \subsubsection{CSPに関する補足説明}

Cross-stage Persistence (CSP) is another primitive of multistage programming, which enable us to embed computed values into a code value.
This is an example of CSP.
\begin{verbatim}
        let plusone = fun x -> x + 1 in
        let a = plusone 2 in  .< a >.
\end{verbatim}
This program evaluates to \verb|.< 3 >.| not  \verb|.< plusone 2 >.|.
This is because the variable \verb|a| is introduced into a code fragment using CSP.
Therefore, the variable \verb|a| is embeded after \verb|a| is calculated.
CSP is very important when we write practival programs 
because CSP enables us to use library functions in code fragments.

% \subsubsection{多段階計算のメリットをべき乗の例を用いて説明する}

The main application of multistage calculi is program optimization.
A famous example is \verb|power| function.
\verb|power| takes two arguments, which are base and exponent.
We can make specialized \verb|power| functions for given exponents with multistage calculi and 
optimize them by unrolling a loop in functions for given exponents.
\red{powerの実際のコードを持ってくるか?}
